R for Clinical Study Reports and Submission

### 2021-07-30 tlf.Rmd
update code to transfer PDF

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
r2rtf:::rtf_convert_format("tlf/bs-1.rtf", output_dir = "tlf")
knitr::include_graphics("tlf/bs-1.pdf")
```

>>>>

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/bs-1.pdf")
```
